### 2019-03-26 thesis_proposal_1/main.tex
thesis proposal 1st draft done
Dora as co-advisor

\documentclass[
% The default document font size, options: 10pt, 11pt, 12pt
11pt, 
% Two side (alternating margins) for binding by default, uncomment to switch to one side
%oneside,
% ngerman for German
english,
% Single line spacing, alternatives: singlespacing, onehalfspacing or doublespacing
onehalfspacing,
% Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
%draft,
% If the document is nolistspacing, onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
onehalfspacing,
% Uncomment to add the list of figures/tables/etc to the table of contents
%liststotoc,
% Uncomment to add the main table of contents to the table of contents
%toctotoc,
% Uncomment to add space between paragraphs
parskip,
% Uncomment to not load the hyperref package
%nohyperref,
% Uncomment to get a line under the header
headsepline,
% Uncomment to place the chapter title next to the number on one line
chapterinoneline,
% Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
%consistentlayout,
% The class file specifying the document structure
]{MastersDoctoralThesis}

@@

% Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\thesistitle{Graphitic carbon suspended nano-wires synthesis through mechanoelectrospinning of photocrosslinkable polymers}

@@

\begin{committee}
\addchaptertocentry{\supervisingcommittee} % Add the the supervising committee to the table of contents
The committee members, hereby, recommend that the proposal by \authorname to be accepted to develop the thesis project as a partial requirement for the degree of \degreename.

@@

\bigskip
\bigskip
\bigskip
\bigskip

\noindent \rule[0.5em]{15em}{0.5pt}\\ % This prints a line for the signature
%\href{http://www.alanaguirre.com}{\supname}
\supname\\
Tecnológico de Monterrey\\
\emph{Principal Advisor}

\bigskip
\bigskip
\bigskip
\bigskip

\noindent \rule[0.5em]{15em}{0.5pt}\\ % This prints a line for the signature
%\href{http://www.alanaguirre.com}{\supname}
Marc \textsc{Madou}\\
Tecnológico de Monterrey\\
\emph{Committee Member}

\bigskip
\bigskip
\bigskip
\bigskip

\noindent \rule[0.5em]{15em}{0.5pt}\\ % This prints a line for the signature
%\href{http://www.alanaguirre.com}{\supname}
Sergio Omar \textsc{Martínez} Chapa\\
Tecnológico de Monterrey\\
\emph{Committee Member}

@@

\bigskip
\bigskip
\bigskip
\bigskip

\noindent \rule[0.5em]{15em}{0.5pt}\\ % This prints a line for the signature
\cosupname \\
\emph{Director of Program in Nanotechnology}\\
School of Engineering and Sciences\\
%\href{http://www.doramedina.com}{\supname}

\bigskip
\bigskip
{\addressname \text{, } \large \today}\\[4cm]

>>>>

\documentclass[
% The default document font size, options: 10pt, 11pt, 12pt
11pt, 
% Two side (alternating margins) for binding by default, uncomment to switch to one side
oneside,
% ngerman for German
english,
% Single line spacing, alternatives: singlespacing, onehalfspacing or doublespacing
onehalfspacing,
% Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
%draft,
% If the document is nolistspacing, onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
onehalfspacing,
% Uncomment to add the list of figures/tables/etc to the table of contents
%liststotoc,
% Uncomment to add the main table of contents to the table of contents
%toctotoc,
% Uncomment to add space between paragraphs
parskip,
% Uncomment to not load the hyperref package
%nohyperref,
% Uncomment to get a line under the header
headsepline,
% Uncomment to place the chapter title next to the number on one line
chapterinoneline,
% Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
%consistentlayout,
% The class file specifying the document structure
]{MastersDoctoralThesis}

@@

% Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\thesistitle{Fabrication of graphitic-carbon suspended nanowires through mechanoelectrospinning of photocrosslinkable polymers}

@@

\begin{committee}
\addchaptertocentry{\supervisingcommittee} % Add the the supervising committee to the table of contents
The committee members, hereby, recommend that the proposal by \authorname \text{ }to be accepted to develop the thesis project as a partial requirement for the degree of \degreename.

@@

\bigskip
\bigskip
\medskip

\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
%\href{http://www.alanaguirre.com}{\supname}
\supname\\
Tecnológico de Monterrey\\
\emph{Principal Advisor}

\bigskip
\bigskip
\medskip

\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
%\href{http://www.alanaguirre.com}{\supname}
\cosupname\\
Tecnológico de Monterrey\\
\emph{Co-Advisor}

\bigskip
\bigskip
\medskip

\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
%\href{http://www.alanaguirre.com}{\supname}
Marc \textsc{Madou}\\
Tecnológico de Monterrey\\
\emph{Committee Member}

\bigskip
\bigskip
\medskip

\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
%\href{http://www.alanaguirre.com}{\supname}
Sergio Omar \textsc{Martínez} Chapa\\
Tecnológico de Monterrey\\
\emph{Committee Member}

@@

\bigskip
\bigskip
\medskip

\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
\cosupname \\
\emph{Director of Program in Nanotechnology}\\
School of Engineering and Sciences\\
%\href{http://www.doramedina.com}{\supname}

\bigskip
{\addressname \text{, } \large \today}\\[0cm]
